UDC 911.3

### 2024-05-11 legal-companies-concentration-and-availability/conference-paper/Paper.Rmd
Split project files into subfolders to prepare for journal article writing on the same topic, adjust paths using here package, #2

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.id = FALSE,
  fig.width = 6.6,
  fig.height = 5)
```

```{r imports, include=FALSE, cache = TRUE}
source("Script.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  root.dir = "../",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.id = FALSE,
  fig.width = 6.6,
  fig.height = 5)
```

```{r imports, include=FALSE, cache = TRUE}
library(here)
source(here("common", "Script.R"))
```
